### 2015-12-07 ch02-qlogms/excitation-design.tex
Small changes
Fix bibliography
stress: periodicity

  This last example illustrates that a least common multiple of real numbers does not always exist.
  Consequently, the generalized multisine of \defref{def:generalized-MS} is not guaranteed to be periodic.

  \TODO{put MATLAB code for each type of signal}

\subsection{Equidistant (Linear) Grid Multisine}
  In many applications, an equidistant frequency grid is used for $u\left( t\right) $ because this fits best with the classical DFT analysis \citep{OppenheimDT,Mandal2007}. It allows to analyze periodic signals on an equidistant frequency grid very efficiently.

@@

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
    Grid & Linear & Logarithmic & Quasi-logarithmic \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbers$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\leq \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\leq \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

@@

\TODO{omrekentabel verschillende grootheden: $F$, $F/\mathrm{dec}$, $F/\mathrm{oct}$, $\alpha$, $\delta f$}

>>>>

  This last example illustrates that a least common multiple of real numbers does not always exist.
  Consequently, the generalized multisine of \defref{def:generalized-MS} is not guaranteed to be periodic.
  In actual implementations with limited numerical precision, this gives rise to signals that are periodic but whose period can be too long to be practically viable for periodic measurements.
  Consequently, it is undesirable to use generalized multisines that have an overly long period.

\subsection{Equidistant (Linear) Grid Multisine}
  In many applications, an equidistant frequency grid is used for $u\left( t\right) $ because this fits best with the classical DFT analysis \citep{OppenheimDT,Mandal2007}. 
  It allows to analyze periodic signals on an equidistant frequency grid very efficiently.
  For such a frequency grid, it is guaranteed that the signal is periodic in the time domain, unlike for the generalized multisines of the previous section.

@@

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
    Grid & Linear & Logarithmic & Quasi-logarithmic \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbers$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\approx \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

@@
